---
title: "Project Title"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

# Problem Definition

简要描述你要解决的问题，包括背景、目标和预期成果。

For this assignment, we selected the Sydney dataset from the Inside Airbnb website. Our research question is: to predict the price category of a property based on its various features. This is a clear classification task, where the variable `price_category` has discrete categories—such as high-end, budget, and mid-range—as prices fall into distinct intervals. Our objective is to assign listings to appropriate price categories based on their attributes, making this a clear classification problem. This research holds significant societal value: as a major global tourist destination, Sydney benefits from our predictive model. Travelers can swiftly find budget-friendly accommodations, while hosts can optimize their listings by analyzing high-priced property characteristics. Overall, analyzing Sydney's Airbnb data provides valuable insights for travelers, governments, and tourism management agencies.


```{r}
# Data import
df <- read_csv("Downloads/listings.csv", 
               col_types = cols(price = col_number()))

# Check the distribution of the price variable
summary(df$price)

# Run your plotting code
ggplot(df, aes(x = price)) +
  geom_histogram(binwidth = 500, fill = "skyblue", color = "black") +
  labs(title = "Price Distribution", x = "Price", y = "Count") +
  theme_minimal()

# Create a price quartile variable, price_category, based on price
df_with_quartiles <- df %>%
  mutate(price_category = ntile(price, 4))

# Check the distribution of the new variable
table(df_with_quartiles$price_category)

# Replace numeric labels with more meaningful descriptions
df_with_quartiles <- df_with_quartiles %>%
  mutate(price_category = case_when(
    price_category == 1 ~ "Q1 (Low)",
    price_category == 2 ~ "Q2 (Medium-Low)",
    price_category == 3 ~ "Q3 (Medium-High)",
    price_category == 4 ~ "Q4 (High)"
  ))

# Check the distribution again to confirm the classification
table(df_with_quartiles$price_category)
```
---


# Data Description

- 数据来源
- 数据集结构（字段、类型、样本量等）
- 主要变量说明

```{r}
# 这是 R 代码，可以直接运行 测试
summary(cars)
plot(cars)
```
---

# Data Cleaning & Feature Engineering
1. Price Column Processing & Outlier Detection
This R code finds the price column, cleans its data by removing non-numeric characters, converts it to a numeric type, and removes any rows where the price is 0 or less. It then performs an outlier analysis based on the IQR method.
```{r}
library(tidyr)
# Re-read the cleaned data from the previous step
df <- read_csv("listings.csv", col_types = cols(.default = "c"))

# Step 1: Find the price column
price_col <- NULL
possible_cols <- names(df)

# Check for 'price' (case-insensitive)
price_col <- possible_cols[str_detect(tolower(possible_cols), "price")][1]
if (is.na(price_col)) {
  # If not found, check for other keywords
  price_keywords <- c('cost', 'amount', 'value', 'fee', 'charge', 'payment')
  for (keyword in price_keywords) {
    found_col <- possible_cols[str_detect(tolower(possible_cols), keyword)][1]
    if (!is.na(found_col)) {
      price_col <- found_col
      break
    }
  }
}

if (is.na(price_col)) {
  stop("Error: Could not find a column representing price.")
}

message(paste0("Using '", price_col, "' as the price column."))

# Step 2: Clean and convert the price column (corrected)
df <- df %>%
  mutate(
    # Remove commas and non-numeric characters, then convert to numeric.
    # `as.numeric` will correctly convert invalid values to `NA`.
    !!sym(price_col) := as.numeric(str_remove_all(str_remove_all(tolower(!!sym(price_col)), ","), "[^\\d.-]"))
  ) %>%
  # Now, filter out rows where the price is NA or <= 0
  filter(!is.na(!!sym(price_col)) & !!sym(price_col) > 0)

message(paste0("Effective price data rows: ", nrow(df)))

# Step 3: Analyze outliers using IQR (will now work correctly)
q1 <- quantile(df[[price_col]], 0.25)
q3 <- quantile(df[[price_col]], 0.75)
iqr <- q3 - q1
lower_bound <- q1 - 1.5 * iqr
upper_bound <- q3 + 1.5 * iqr

outliers <- df %>% filter(!!sym(price_col) < lower_bound | !!sym(price_col) > upper_bound)

message("\nOutlier Analysis:")
message(paste0("Interquartile Range (IQR): ", round(iqr, 2)))
message(paste0("Outlier Lower Bound: ", round(lower_bound, 2)))
message(paste0("Outlier Upper Bound: ", round(upper_bound, 2)))
message(paste0("Number of outliers: ", nrow(outliers), " (", round(nrow(outliers) / nrow(df) * 100, 2), "% of data)"))

# Step 4: Save the further cleaned data
write_csv(df, "cleaned_data.csv")
message("\nUpdated 'cleaned_data.csv' saved with prices > 0.")

```
2. Feature Engineering: Price Categorization
This section adds a new categorical column, price_class, to the dataset based on the price value. This new feature can be useful for further analysis or machine learning models.
```{r}
# Re-read the cleaned data from the previous step
df <- read_csv("cleaned_data.csv", col_types = cols(.default = "c"))

# Find the price column again
price_col <- names(df)[str_detect(tolower(names(df)), "price")][1]

# Check if the price column was found
if (is.na(price_col)) {
  stop("Error: Could not find a column representing price.")
}

message(paste0("Using '", price_col, "' as the price column."))

# Step 1: Ensure the price column is numeric before creating 'price_class'
# This is a crucial step to prevent errors
df <- df %>%
  mutate(
    # Safely convert the price column to numeric,
    # invalid parsing will result in NA
    price_numeric = as.numeric(!!sym(price_col)),
    
    # Create the new 'price_class' column based on the numeric price
    price_class = case_when(
      is.na(price_numeric) | price_numeric <= 0 ~ "Invalid Price",
      price_numeric < 150 ~ "[0,150)",
      price_numeric < 300 ~ "[150,300)",
      TRUE ~ "[300,+)"
    )
  )

# Step 2: Reorder columns to place 'price_class' at the beginning
df <- df %>%
  select(price_class, everything(), -price_numeric)

# Step 3: Save the data with the new column
write_csv(df, "cleaned_data_with_price_class.csv")
message("\nFile saved to 'cleaned_data_with_price_class.csv' with new 'price_class' column.")

```
3. Missing Value Imputation
This R code block replicates the final data cleaning step, which involves imputing missing values with specific placeholders (-1 for numeric columns and 'NA' for non-numeric columns). It also includes a function to calculate the "missing rate" based on these placeholders.
```{r}
# Load necessary libraries
# You might need to install these packages first: install.packages("tidyverse")
library(readr)
library(dplyr)
library(ggplot2)
library(stringr)

# Re-read the data
# suppressWarnings is added here as `read_csv` might generate warnings
df <- suppressWarnings(read_csv("cleaned_data_with_price_class.csv", col_types = cols(.default = "c")))

# Step 1: Identify numeric and non-numeric columns using the Python logic
numeric_cols <- character(0)
non_numeric_cols <- character(0)

for (col in names(df)) {
  sample <- df[[col]][!is.na(df[[col]]) & df[[col]] != "NA"][1:100]
  if (length(sample) > 0) {
    # suppressWarnings is used here to hide the 'NAs introduced by coercion' warnings
    numeric_count <- suppressWarnings(sum(!is.na(as.numeric(sample))))
    if (numeric_count / length(sample) > 0.8) {
      numeric_cols <- c(numeric_cols, col)
    } else {
      non_numeric_cols <- c(non_numeric_cols, col)
    }
  } else {
    non_numeric_cols <- c(non_numeric_cols, col)
  }
}

# Step 2: Impute missing values
df_imputed <- df %>%
  mutate(
    # Impute NA in numeric columns with -1
    across(all_of(numeric_cols), ~replace_na(as.numeric(.x), -1)),
    # Impute NA in non-numeric columns with 'NA'
    across(all_of(non_numeric_cols), ~replace_na(.x, 'NA'))
  )

# Step 3: Save the final cleaned data
write_csv(df_imputed, "cleaned_data_with_price_class_no_na.csv")
message("\nFinal cleaned data saved to 'cleaned_data_with_price_class_no_na.csv'.")
message(paste0("Found ", length(numeric_cols), " numeric columns."))
message(paste0("Found ", length(non_numeric_cols), " non-numeric columns."))

# Step 4: Create a function to calculate missing rates
calculate_missing_rates <- function(data) {
  missing_rates <- sapply(names(data), function(col) {
    # Check for -1 in columns that have been correctly converted to numeric
    if (is.numeric(data[[col]])) {
      sum(data[[col]] == -1) / nrow(data)
    } else {
      # Check for 'NA' or '-1' in non-numeric columns
      sum(data[[col]] %in% c('NA', '-1')) / nrow(data)
    }
  })
  sort(missing_rates * 100, decreasing = TRUE)
}

missing_rates <- calculate_missing_rates(df_imputed)
message("\nMissing rates per column (high to low):")
print(missing_rates)
```
Following this, I swapped the positions of the `id` and `price_class` columns. Then, I performed further manual data cleaning in Excel:

1.  I atomicized the `host_location` column, making the values as granular and indivisible as possible.
2.  I filtered and removed rows where column data was misaligned. I also deleted columns that were not very useful for Exploratory Data Analysis (EDA), including but not limited to:
    * `listing_url`
    * `scrape_id`
    * `description`
    * `neighborhood_overview`
    * `picture_url`
    * `host_id`
    * `host_url`
    * `host_name`
    * `host_about`
    * `host_thumbnail_url`
    * `host_picture_url`
    * `neighbourhood_group_cleansed`
    * `calendar_updated`

These features were removed either because they had little analytical value or because their missing data rate was close to 100%.

# Exploratory Data Analysis (EDA)
初步 EDA : 变量之间的关系

可视化结果（直方图、散点图、箱线图等）

# Project Plan Summary
